TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
scheduling, SIMD vs. MIMD talk in background

Example Citation\cite{Chain, Mementos, Aware, Dino}!

@@

More text after the picture to show how that looks...

@@

\section{What we did} % TODO change title
Mutexes - Emily\\
Round Robin (alternatives, on reboot)\\
SIMD vs MIMD\\
SIMD w/ channels (you don't get your own registers...etc -
    just channels, since intermittent)\\

>>>>

%Example Citation\cite{Chain, Mementos, Aware, Dino}!

@@

%More text after the picture to show how that looks...

@@

\section{What we did} % TODO change title
Mutexes - Emily\\

TAPIR has a round robin scheduling algorithm. At the end of a task, the compiler
inserts a jump back to the scheduler task, where the next task in the list is
the one to be executed. An alternate scheduling model that was considered was
a context switch on reboot instead of at the end of each task. The main drawback
of using a reboot-based scheduler is that, because power failure is the common
case, there is a high chance of reducing or halting forward progress altogether
because one thread holds a lock that all of the other threads need but cannot
complete. For that reason the design specifies end of task, so each task has
an opportunity to use a shared resource and release any locks before a power-
intensive context switch occurs. Additionally, a round robin scheduler was 
chosen for this design because it is simple to implement and uses only one index counter,
very little power or memory overhead as compared to other scheduling algorithms. It is 
critical for multithreading in Chain to not add significant power and memory
overhead in scheduling over conventional Chain so that the workload can
make as much forward progress as possible on one charge cycle.

When designing threading in Chain, the shared memory model is a main indicator 
of the threaded execution model. The two most probable options when designing 
TAPIR were a SIMD execution model of \textit{Thread Pools}, or a MIMD 
traditional multiprogramming model. The Thread Pool design makes use of task 
code duplication by explicitly forking a number of chain programs, all of which 
run simultaneously on the scheduler on arrayed data. This option is useful 
multiple data streams from I/O in embedded applications that need to be 
processed before new data overrides the I/O device. Additionally, the Thread 
Pool model makes sharing memory more regular by using multiple copies of the 
same thread. However, this option is not as general purpose. The TAPIR design 
ultimately settled on a multiprogramming model, because this allows for the 
programmer to explictly program unique chain programs with shared or discrete 
data structures on the same system. However, this execution model requires a
more structured locking mechanism to avoid RMW during execution.

SIMD w/ channels (you don't get your own registers...etc -
    just channels, since intermittent)\\
